Effect of quality-adjusted production function inputs

### 2015-05-13 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
var names now use . instead of _

<<Pre-econometric graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Pre-econometric data.", warning=FALSE>>=
# Melt the data
mdata_preeconometric <- melt(historicalData, 
                             measure.vars = c("kPerGDP_unadj", "lPerGDP_unadj", "ePerGDP_unadj",
                                              "kPerGDP_adj", "lPerGDP_adj", "ePerGDP_adj"),
                             variable.name = "variable",
                             value.name = "value")
# Add a column to say whether the variable is Unadjusted or Quality-adjusted based on variable name
mdata_preeconometric$adjusted <- lapply(mdata_preeconometric$variable, function(x) {
  suffix <- unlist(strsplit(as.character(x), split="[_]")) [2]
  if (suffix == "unadj"){
    return("Unadjusted")
  } else if (suffix == "adj"){
    return("Quality-adjusted")
  } else {
    stop(paste("Unknown suffix:", suffix))
  }
})
# Fix levels
mdata_preeconometric$adjusted <- relevelFactor(as.factor(as.character(mdata_preeconometric$adjusted)), 
                                               c("Unadjusted", "Quality-adjusted"))
mdata_preeconometric$Country <- relevelFactor(as.factor(mdata_preeconometric$Country), 
                                              c("PT", "UK"))
# Now make the plot
historicalPlot(mdata_preeconometric, 
               mapping=aes(x=Year, y=value, group=variable, linetype=variable), 
               facet_formula = Country ~ adjusted, 
               line_types = c(2,4,3, 2,4,3)) + 
  xlab("") + 
  ylab("Indexed (1960=1)")
@

>>>>

<<Pre-econometric graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Pre-econometric data.", warning=FALSE>>=
# Melt the data
mdata_preeconometric <- melt(historicalData, 
                             measure.vars = c("kPerGDP.unadj", "lPerGDP.unadj", "ePerGDP.unadj",
                                              "kPerGDP.adj", "lPerGDP.adj", "ePerGDP.adj"),
                             variable.name = "variable",
                             value.name = "value")
# Add a column to say whether the variable is Unadjusted or Quality-adjusted based on variable name
mdata_preeconometric$adjusted <- lapply(mdata_preeconometric$variable, function(x) {
  suffix <- unlist(strsplit(as.character(x), split="[.]")) [2]
  if (suffix == "unadj"){
    return("Unadjusted")
  } else if (suffix == "adj"){
    return("Quality-adjusted")
  } else {
    stop(paste("Unknown suffix:", suffix))
  }
})
# Fix levels
mdata_preeconometric$adjusted <- relevelFactor(as.factor(as.character(mdata_preeconometric$adjusted)), 
                                               c("Unadjusted", "Quality-adjusted"))
mdata_preeconometric$Country <- relevelFactor(as.factor(mdata_preeconometric$Country), 
                                              c("PT", "UK"))
# Now make the plot
historicalPlot(mdata_preeconometric, 
               mapping=aes(x=Year, y=value, group=variable, linetype=variable), 
               facet_formula = Country ~ adjusted, 
               line_types = c(2,4,3, 2,4,3)) + 
  xlab("") + 
  ylab("Indexed (1960=1)")
@
